Large scale risks from pesticides in small streams

### 2016-10-20 article.tex
results text

The distribution of sampling sites across catchment sizes indicated a disproportionally low number of sites of catchments below $10~km^2$, with
most sampling sites having catchment sizes between 10 and 25 $km^2$ (Figure~\ref{fig:fig3}).

>>>>

The distribution of sampling sites across catchment sizes indicated a disproportionally low number of sites with catchments below $10~km^2$, with
most sampling sites having catchment sizes between 10 and 25~$km^2$ (Figure~\ref{fig:fig3}).
